Measuring Subgroup Preferences in Conjoint Experiments\footnote{We thank Benjamin Lauderdale, Jamie Druckman, Yusaku Horiuchi, the editor, and anonymous reviewers for feedback on this manuscript.}

### 2019-04-16 manuscript.Rnw
trim abstract for resubmission

{\abstract Conjoint analysis is now a common tool for studying political preferences. The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as political candidates or public policies. Most conjoint analyses rely upon a fully randomized conjoint design to generate average marginal component effects (AMCEs). These measure the degree to which a given value of a conjoint profile feature increases, or decreases, people’s support for the overall profile relative to a baseline, averaging across all respondents and all other profile features. While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of preferences or favorability. This often means comparing AMCEs among subgroups of respondents. We show that using conditional AMCEs to describe the degree of agreement among subgroups can be misleading as regression interactions are sensitive to the reference category used in the analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from the published literature and provide suggestions for improved reporting and interpretation using two quantities of interest: the marginal mean and the omnibus F-test. Given the accelerating use of conjoint analyses in political science, we offer advice for best practice in the analysis and presentation of conjoint experiments.}

>>>>

{\abstract Conjoint analysis is a common tool for studying political preferences. The method disentangles patterns in respondents' favorability toward complex, multidimensional objects, such as candidates or policies. Most conjoints rely upon a fully randomized design to generate average marginal component effects (AMCEs). These measure the degree to which a given value of a conjoint profile feature increases, or decreases, respondents' support for the overall profile relative to a baseline, averaging across all respondents and other features. While the AMCE has a clear causal interpretation (about the \textit{effect} of features), most published conjoint analyses also use AMCEs to describe \textit{levels} of favorability. This often means comparing AMCEs among respondent subgroups. We show that using conditional AMCEs to describe the degree of subgroup agreement can be misleading as regression interactions are sensitive to the reference category used in the analysis. This leads to inferences about subgroup differences in preferences that have arbitrary sign, size, and significance. We demonstrate the problem using examples drawn from published articles and provide suggestions for improved reporting and interpretation using marginal means and an omnibus F-test. Given the accelerating use of these designs in political science, we offer advice for best practice in analysis and presentation of results.}

### 2019-04-16 manuscript.tex
trim abstract for resubmission

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## R version 3.5.3 (2019-03-11)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 7 x64 (build 7601) Service Pack 1
## 
## Matrix products: default
## 
## locale:
## [1] LC_COLLATE=English_United Kingdom.1252 
## [2] LC_CTYPE=English_United Kingdom.1252   
## [3] LC_MONETARY=English_United Kingdom.1252
## [4] LC_NUMERIC=C                           
## [5] LC_TIME=English_United Kingdom.1252    
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] gridExtra_2.3 ggplot2_3.1.1 cregg_0.3.1   rio_0.5.16   
## 
## loaded via a namespace (and not attached):
##  [1] zip_2.0.1         Rcpp_1.0.1        cellranger_1.1.0 
##  [4] pillar_1.3.1      compiler_3.5.3    plyr_1.8.4       
##  [7] forcats_0.4.0     tools_3.5.3       digest_0.6.18    
## [10] lattice_0.20-38   evaluate_0.13     tibble_2.1.1     
## [13] gtable_0.3.0      ggstance_0.3.1    pkgconfig_2.0.2  
## [16] rlang_0.3.4       Matrix_1.2-17     openxlsx_4.1.0   
## [19] curl_3.3          haven_2.1.0       xfun_0.6         
## [22] withr_2.1.2       stringr_1.4.0     knitr_1.22       
## [25] hms_0.4.2         lmtest_0.9-36     grid_3.5.3       
## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
## [31] readxl_1.3.1      foreign_0.8-71    reshape2_1.4.3   
## [34] readr_1.3.1       magrittr_1.5      codetools_0.2-16 
## [37] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
## [40] xtable_1.8-3      colorspace_1.4-1  labeling_0.3     
## [43] sandwich_2.5-1    survey_3.35-1     stringi_1.4.3    
## [46] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4     
## [49] zoo_1.8-5
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## R version 3.5.3 (2019-03-11)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 7 x64 (build 7601) Service Pack 1
## 
## Matrix products: default
## 
## locale:
## [1] LC_COLLATE=English_United Kingdom.1252 
## [2] LC_CTYPE=English_United Kingdom.1252   
## [3] LC_MONETARY=English_United Kingdom.1252
## [4] LC_NUMERIC=C                           
## [5] LC_TIME=English_United Kingdom.1252    
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] gridExtra_2.3 ggplot2_3.1.1 cregg_0.3.1   rio_0.5.16   
## 
## loaded via a namespace (and not attached):
##  [1] zip_2.0.1         Rcpp_1.0.1        cellranger_1.1.0 
##  [4] pillar_1.3.1      compiler_3.5.3    plyr_1.8.4       
##  [7] forcats_0.4.0     tools_3.5.3       digest_0.6.18    
## [10] lattice_0.20-38   evaluate_0.13     tibble_2.1.1     
## [13] gtable_0.3.0      ggstance_0.3.1    pkgconfig_2.0.2  
## [16] rlang_0.3.4       Matrix_1.2-17     openxlsx_4.1.0   
## [19] curl_3.3          haven_2.1.0       xfun_0.6         
## [22] withr_2.1.2       stringr_1.4.0     knitr_1.22       
## [25] hms_0.4.2         lmtest_0.9-36     grid_3.5.3       
## [28] data.table_1.12.2 R6_2.4.0          survival_2.44-1.1
## [31] readxl_1.3.1      foreign_0.8-71    magrittr_1.5     
## [34] splines_3.5.3     scales_1.0.0      assertthat_0.2.1 
## [37] xtable_1.8-3      colorspace_1.4-1  sandwich_2.5-1   
## [40] survey_3.35-1     stringi_1.4.3     lazyeval_0.2.2   
## [43] munsell_0.5.0     crayon_1.3.4      zoo_1.8-5
\end{verbatim}
\end{kframe}
\end{knitrout}
